---
title: 'biokNN: A bi-objective imputation method for multilevel data in R'
author:
  # see ?rjournal_article for more information
  - name: Maximiliano Cubillos
    affiliation: Aarhus University
    # address:
    # - line 1
    # - line 2
    # url: https://journal.r-project.org
    # orcid: 0000-0002-9079-593X
    email:  mcub@econ.au.dk
  - name: Jesper N. Wulff
    email: jwulff@econ.au.dk
    affiliation: Aarhus University
  - name: Sanne Wøhlk
    email: sanw@econ.au.dk
    affiliation: Aarhus University
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
  
# per R journal requirement, the bib filename should be the same as the output 
# tex file. Don't forget to rename the bib file and change this example value.
bibliography: biokNN.bib

output: rticles::rjournal_article
---
```{r, echo=FALSE, warning = FALSE}
library(biokNN)
library(dplyr)
library(ggplot2)
library(mice)
```



## Introduction

Introductory section which may include references in parentheses
[@R], or cite a reference such as @R in the text.

## Overview of biokNN

Functions. Most important: biokNN.impute. Explain parameters.

## Example with simulated data 

```{r, echo = TRUE}
set.seed(12345)
df <- create.multilevel(nClass = 25, nVars = 1, classMean = 10, classSD = 0, 
                        beta0 = 0, tau0 = 1, beta = c(1), tau = c(1), sigma2 = 1)
head(df)
```


```{r, echo=FALSE}
df_obs <- df
clust_var <- df_obs$class
df_obs$class <- NULL
df_amp <- ampute(df_obs, prop = 0.3, mech = "MCAR")
df_miss <- df_amp$amp 
df_miss$class <- clust_var 
df_miss <- df_miss %>% select(class, everything())
df_obs <- df_obs %>% mutate(class = clust_var) %>% select(class, everything())

```


```{r, echo = TRUE, fig.cap='The logo of R.', out.width='2in', fig.align='center', fig.pos='htbp'}
biokNN::plot.missing(df_miss, 'class')
```




## Data structure



## Recommendations in using biokNN package


## Section title in sentence case

<!-- This section may contain a figure such as Figure \ref{fig:Rlogo}. -->

```{r, Rlogo, echo=FALSE, eval = FALSE, fig.cap='The logo of R.', out.width='2in', fig.align='center', fig.pos='htbp'}
knitr::include_graphics('Rlogo.pdf')
```


<!-- There will likely be several sections, perhaps including code snippets, such as: -->

```{r}
x <- 1:10
```

## Summary

This file is only a basic article template. For full details of _The R Journal_ style and information on how to prepare your article for submission, see the [Instructions for Authors](https://journal.r-project.org/share/author-guide.pdf).

### About this format and the R Journal requirements

`rticles::rjournal_article` will help you build the correct files requirements: 

* A R file will be generated automatically using `knitr::purl` - see
https://bookdown.org/yihui/rmarkdown-cookbook/purl.html for more information.
* A tex file will be generated from this Rmd file and correctly included in
`RJwapper.tex` as expected to build `RJwrapper.pdf`.
* All figure files will be kept in the default rmarkdown `*_files` folder. This
happens because `keep_tex = TRUE` by default in `rticles::rjournal_article`
* Only the bib filename is to modifed. An example bib file is included in the
template (`RJreferences.bib`) and you will have to name your bib file as the
tex, R, and pdf files.
